On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-05-21 Manuscript/manuscript.tex
Minor edits

\begin{figure}[tbp]
  \centering
  \includegraphics{2019vs2022BarGraph}
  \caption{The reaction times from 2019 and 2022}
  \label{fig:2019vs2022Graph}
\end{figure}

@@

>>>>

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{2019vs2022BarGraph}
  \caption{The reaction times from 2019 and 2022 World Track and Field
  Championship. ``H'', ``S'', and``F'' refer to the heats, semifinals, and finals
  respectively.}
  \label{fig:2019vs2022Graph}
\end{figure}
\of{I included this here for now, but feel free to change the location.  I will
add references to it and explanation of it along with some descriptive statistics about
the size and mean/median,std dev, size of the data.}
